Placeholder for article 3

### 2025-01-21 analysis/paper/paper.qmd
Corrected missing graphs and render.

gravettian_graphs <- ggpubr::ggarrange(gravettian_scatter, gravettian_stats_weight, labels = c("c1", "c2"), ncol = 2, common.legend = TRUE, legend = "bottom")

@@

proto_graphs <- ggpubr::ggarrange(proto_scatter, proto_stats_weight, labels = c("b1", "b2"), ncol = 2, common.legend = TRUE, legend = "bottom")

@@

solutrean_graphs <- ggpubr::ggarrange(solutrean_scatter, solutrean_stats_weight, labels = c("a1", "a2"), ncol = 2, common.legend = TRUE, legend = "bottom")

>>>>

ggpubr::ggarrange(gravettian_scatter, gravettian_stats_weight, labels = c("a", "b"), ncol = 2, common.legend = TRUE, legend = "bottom")

@@

ggpubr::ggarrange(proto_scatter, proto_stats_weight, labels = c("b1", "b2"), ncol = 2, common.legend = TRUE, legend = "bottom")

@@

ggpubr::ggarrange(solutrean_scatter, solutrean_stats_weight, labels = c("a", "b"), ncol = 2, common.legend = TRUE, legend = "bottom")
